\documentclass{article}

\usepackage{amsmath} % math stuff
\usepackage{amssymb} % math stuff
\usepackage{array} % equations and stuff
\usepackage{bm} % bold math
%\usepackage{caption} % suppressed table numbering; incompatible with revtex, and longtable, I think
\usepackage{comment} % comment environment
%\usepackage{enumitem} % customization of enumeration, itemize, and description
\usepackage[T1]{fontenc} % font encoding for special characters, must also use scalable font package
\usepackage[margin=0.8in]{geometry} % paper sizes and margins (but be careful not to mess up pre-defined pages)
\usepackage{graphicx} % for graphics
%\usepackage{helvet} % default font is the helvetica postscript font
\usepackage{layouts} % print units like widths
\usepackage{lipsum} % lorem ipsum filler text
\usepackage{lmodern} % scalable font?
\usepackage{longtable} % multi-page tables
\usepackage{mathrsfs} % math script font
\usepackage{mhchem} % easier chemical formula
\usepackage{microtype} % allows disabling of ligatures
%\usepackage{newcent} % new century schoolbook font
\usepackage{nicefrac}
\usepackage{parskip} % removes paragraph indentation, and adjusts paragraph skip, as well as list items
\usepackage{pdfpages} % add pdf files as pages
%\usepackage{setspace} % adjust text spacing and indents
\usepackage{siunitx} % decimal alignment
\usepackage{subfigure} % divided figures
%\usepackage{tabu} % extra table options
\usepackage{textcomp} % symbols
\usepackage{threeparttablex} % better footnotes with longtable
\usepackage{titling} % title placement
\usepackage{ulem} % strikethrough text
%\usepackage{url} % superceded by hyperref
\usepackage{verbatim} % verbatim environment
\usepackage{xcolor} % colors and color boxes
\usepackage{xspace} % commands that don't eat up white space
\usepackage{hyperref} % links and page setup; should always come last

\hypersetup{
	bookmarks=true,
	colorlinks=true,
	citecolor=blue,
	linkcolor=blue,
	urlcolor=blue,
	pdfstartview={XYZ null null 1.0} % default open view is 100%
}

\DisableLigatures[f,t]{encoding = T1} % disable ff, fi, fl, tt ligatures, without f option, it also disables -- = endash
\renewcommand{\arraystretch}{1.1} % extra vertical space in tables

\begin{document}

\pagestyle{empty} % don't number pages

% custom title
\begin{center}
{\LARGE Classic Riddler}

\vspace{0.15in}

{\Large 23 October 2020}
\end{center}


\section*{Riddle:}

This season, on the way to winning her fourth WNBA championship in her 17-year career, Sue Bird made approximately 50 percent of her field goal attempts.
Suppose she and Seattle Storm teammate Breanna Stewart are interested in testing whether Bird has a ``hot hand''---that is, if her chances of making a basket depend on whether or not her previous shot went in.
Bird happens to know that her chances of making any given shot is always 50 percent, independent of her shooting history, but she agrees to perform an experiment.

In each trial of the experiment, Bird will take three shots, while Stewart will record which shots Bird made or missed.
Stewart will then look at all the trials that had at least one shot that was immediately preceded by a made shot.
She will randomly pick one of these trials and then randomly pick a shot that was preceded by a made shot.
(If there was only one such shot to pick from, she will choose that shot.)

What is the probability that Bird made the shot that Stewart picked?

\section*{Solution:}

For three shots in each trial, there are only 8 ($=2^{3}$) possible outcomes for each trial.
I list them below, using 1s for scores and 0s for misses:

\begin{center}
\begin{tabular}{cc}
0-0-0 & 0-0-1 \\
0-1-0 & 0-1-1 \\
1-0-0 & 1-0-1 \\
1-1-0 & 1-1-1
\end{tabular}
\end{center}

Each of these possible outcomes is equally likely for any trial.
Six of these have a made shot preceding some other shot.
Of these six, three (0-1-0, 1-0-0, and 1-0-1) have a made shot followed only by a missed shot, so by choosing one of these trials, Stewart will pick a missed shot.
Two (0-1-1 and 1-1-1) have made shots followed only by made shots, and by choosing either of these trials, Stewart will pick a made shot.
The fifth (1-1-0) has both a missed and a made shot after a made shot.
Since the choice of shot within a trial is evenly distributed, Stewart has a 50\% chance of picking either a missed or made shot.
So in a sense, there is a 3\,\nicefrac{1}{2} out of 6 chance, or \nicefrac{7}{12}, of picking a missed shot, and a 2\,\nicefrac{1}{2} out of 6 chance, or \nicefrac{5}{12}, of picking a made shot.
So the solution is
\fcolorbox{red}{white}{\bf \nicefrac{5}{12}}\,.



\end{document}