\documentclass{article}


\usepackage{amsmath} % math stuff
\usepackage{amssymb} % math stuff
\usepackage{array} % equations and stuff
\usepackage{bm} % bold math
%\usepackage{caption} % suppressed table numbering; incompatible with revtex, and longtable, I think
\usepackage{comment} % comment environment
%\usepackage{enumitem} % customization of enumeration, itemize, and description
\usepackage[T1]{fontenc} % font encoding for special characters, must also use scalable font package
\usepackage[margin=0.8in]{geometry} % paper sizes and margins (but be careful not to mess up pre-defined pages)
\usepackage{graphicx} % for graphics
%\usepackage{helvet} % default font is the helvetica postscript font
\usepackage{lipsum} % lorem ipsum filler text
\usepackage{lmodern} % scalable font?
\usepackage{longtable} % multi-page tables
\usepackage{mathrsfs} % math script font
\usepackage{microtype} % allows disabling of ligatures
%\usepackage{newcent} % new century schoolbook font
\usepackage{parskip} % removes paragraph indentation, and adjusts paragraph skip, as well as list items
%\usepackage{setspace} % adjust text spacing and indents
\usepackage{siunitx} % decimal alignment
\usepackage{subfigure} % divided figures
\usepackage{tabu} % extra table options
\usepackage{textcomp} % symbols
\usepackage{threeparttablex} % better footnotes with longtable
\usepackage{titling} % title placement
%\usepackage{url} % superceded by hyperref
\usepackage{verbatim} % verbatim environment
\usepackage{xcolor} % colors and color boxes
\usepackage{xspace} % commands that don't eat up white space
\usepackage{hyperref} % links and page setup; should always come last

\hypersetup{
	bookmarks=true,
	colorlinks=true,
	citecolor=blue,
	linkcolor=blue,
	urlcolor=blue,
	pdfstartview={XYZ null null 1.0} % default open view is 100%
}

\DisableLigatures[f]{encoding = *, family = * } % disable ff, fi, fl ligatures, without f option, it also disables -- = endash

%\setlength{\droptitle}{-4em} % remove huge white space above title

%\title{Riddler Express}
%\author{}
%\date{13 December 2019}

\begin{document}

\pagestyle{empty} % don't number pages

%\maketitle

% custom title
\begin{center}
{\LARGE Riddler Express}

\vspace{0.15in}

{\Large 6 December 2019}
\end{center}


\section*{Riddle:}

After being ambushed by the forces of the First Order on the planet Jakku, the droid BB-8 narrowly escaped and requires immediate help.
Fortunately, there is one person (named Rey) on the planet who can help BB-8, but they’ve never met and BB-8 has no idea where Rey is located.

Even if BB-8 did know where Rey was, what’s the probability that BB-8 could reach her within 24 hours?
Assume Jakku has a radius of 4,000 miles (similar to Earth) and that BB-8 rolls along at a speed of 3 miles per hour.



\section*{Solution:}

The area that BB-8 could cover is basically a circle around its starting point.
Its maximum travel distance is 3~mph $\times$ 24~hours, or 72~miles.
I will here assume that it would be in sight of Rey within a distance of about 2~miles, so the total coverage radius is generously 74~miles.
The area of the circle is $\pi(74~\mathrm{mile})^{2}$, or $1.72\times10^{4}$~sq.~miles.
The surface area of the planet is $4\pi(4,000~\mathrm{mile})^{2}$, or $2.01\times10^{8}$~sq.~miles.
The probability is just the ratio of these two areas, so the solution is $8.556\times10^{-5}$, or
\fcolorbox{red}{white}{\bf0.0086\%}\,.



\end{document}